```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE, results='hide')
```

# CFQ Analyses for IARPA Final Report
**Creator(s)**: _Joe Tidwell_
**Date**: _20150618_

```{r setup, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(ggplot2)
library(foreach)
library(doMC)
# library("multicore", quietly=TRUE)
# registerDoMC(max(multicore:::detectCores()-6,2)) # use all cores minus 2
registerDoMC(28)

source("~/ACE/global_vars.R")
source(file.path(kRootPath, "util", "load_data.R"), chdir=T)
source(file.path(kRootPath, "fitting", "interval_fitting_funcs.R"), chdir=T)
source(file.path(kRootPath, "forecast", "method_consensus_dist.R"), chdir=T)

options(stringsAsFactors = FALSE)
path.mydata <- "~/git/QES2/data"
```



```{r}
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#### Generic Functions
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


# Switchable generic cumulative distribution function
CDF <- function(dist.name, ...) {
  return(
    switch(dist.name,
           normal = pnorm(...),
           beta   = pbeta(...),
           gamma  = pgamma(...)
    )
  )
}

# Switchable generic density function
PDF <- function(dist.name, ...) {
  return(
    switch(dist.name,
           normal = dnorm(...),
           beta   = dbeta(...),
           gamma  = dgamma(...)
    )
  )
}


# Generic Inverse Cumulative Distribution Function
QDF <- function(dist.name, ...){
  switch(dist.name,
         normal = qnorm(...),
         beta   = qbeta(...),
         gamma  = qgamma(...)
  )
}

# Generic Sampler
RDF <- function(dist.name, ...){
  switch(dist.name,
         normal = rnorm(...),
         beta   = rbeta(...),
         gamma  = rgamma(...)
  )
}
```


```{r}
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#### Get set of closed IFPS
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

# Get closed IFPs
ifp.key <- as.data.table(read.csv(file.path(path.mydata, "ifp_key-SV.csv")))
ifp.key <- ifp.key[status=="closed",]
setkey(ifp.key, ifp_idx)
ifp.data <- as.data.table(read.csv(file.path(kRootPath, "data", "ifps", "ifps.yr4.csv")))
ifp.data <- ifp.data[, list(ifpid, q_status, q_type, date_closed)]
setkey(ifp.data, ifpid)

ifp.data <- ifp.data[ifp.key][date_closed!="NULL"]


ifp.data[,ifp_id:=paste(ifpid,q_type,sep="-")]
ifp.data <- ifp.data[q_status=="closed",]
ifp.data[, date_closed:=as.Date(date_closed)-1]

# Get resolution values
IFP.res <- data.table(read.csv(file.path(path.mydata,"lum_ifp_data.csv")))
IFP.res[,IFPID:=as.character(IFPID)]
ifp.data[, ifpid:=as.character(ifpid)]
setkey(IFP.res, IFPID)
setkey(ifp.data,ifpid)

ifp.data <- IFP.res[,list(IFPID,Outcome)][ifp.data]
```

```{r}
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#### Data Wrangling
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

load(file.path(path.mydata,"allfits.Rdata"))
fcasts <- all.fits

# Only non-roller conditions
fcasts  <- fcasts[!(type%in%c("rolling","rollingCtl"))] 

# for some reason 1448 is duplicated
tmp <- ifp.data[IFPID=="1448"][1]
ifp.data <- cbind(ifp.data[IFPID!="1448"],tmp)

# merge with ifp.data
# ifp.data <- ifp.data[IFPID!="1419"]
setkey(fcasts, ifp_idx)
setkey(ifp.data, IFPID)
fcasts <- ifp.data[fcasts]

names.bins <- grep("bin_", names(fcasts), fixed=TRUE, value=TRUE)
names.ctpts <- grep("ctpt_", names(fcasts), fixed=TRUE, value=TRUE)

# Convert date outcomes to numeric
fcasts[dist=="gamma" & Outcome!="",Outcome:=as.numeric(as.Date(Outcome))]
fcasts[, Outcome:=as.numeric(Outcome)]

# Remove any foracsts without specified outcomes
# fcasts <- fcasts[!is.na(Outcome),]
# fcasts[,Outcome:=as.numeric(Outcome)]


# Error
fcasts[,SS.tot:=2*apply(fcasts[,.SD,.SDcols=names.ctpts],1,var,na.rm=TRUE)]
fcasts[, SS.fit := SS.tot - sse]
fcasts[, R.sq := 1-(sse/SS.tot)]


# c(length(fcasts[,unique(IFPID)])) 


# c(fcasts[,unique(IFPID)][,.N], 
#   fcasts[,.N], fcasts[,mean(R.sq)], fcasts[sse!=42,.N], fcasts[R.sq<=0,.N],
#   )


```

## Raw Data Summary


|                          |                                                          |
|--------------------------|----------------------------------------------------------|
| Unique IFPs              | `r length(fcasts[,unique(IFPID)])`                       |
| Closed (scorable) IFPS   | `r ifp.data[Outcome!="", .N]`                            |
| Unique Forecasters       | `r length(fcasts[,unique(user_id)])`                     |
| Unique Forecasts         | `r fcasts[,.N]`                                          |
| Unfittable Forecasts     | `r fcasts[sse==42,.N]`                                   |
| % Unfittable             | `r round(fcasts[sse==42,.N]/fcasts[,.N],4)*100`          |
| Mean $R^2$               | `r fcasts[,mean(R.sq)]`                                  |
| # $R^2 < 0$              | `r fcasts[R.sq<0,.N]`                                    |
| % $R^2 < 0$              | `r round(fcasts[R.sq<0,.N]/fcasts[,.N],4)*100`           |
| # Forecasts after closed | `r fcasts[as.Date(date_closed)<=as.Date(fcast_date),.N]` |
|                          |                                                          |


```{r}
# Drop 'unfittable'
fcasts <- fcasts[sse!=42,]
# Drop neg Rsq
fcasts <- fcasts[R.sq>0,]

# Adjust outcome (true.score) for date IFPs by date forecast made, and betas
fcasts[value_type=="date" & !is.na(Outcome) ,true.score:=Outcome-as.numeric(as.Date(fcast_date))]
fcasts[value_type!="date",true.score:=Outcome]
fcasts[dist=="beta",true.score:=Outcome/100]


# Drop forecasts made after close
fcasts <- fcasts[as.Date(date_closed)>=as.Date(fcast_date)]

# FOR SOME REASON MANY DATE FORECASTS HAVE NEGATIVE CUTPOINTS... WTF? FIND OUT WHY
fcasts <- fcasts[!(dist=="gamma" & ctpt_0<0)]

# fcasts <- fcasts[!is.na(true.score)]

```

```{r, eval=FALSE}
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#### CRPS
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

scaleUnit <- function(x) {
  (x-min(x, na.rm=TRUE))/(max(x, na.rm=TRUE)-min(x, na.rm=TRUE))
}

GneitingCRPS <- function(distribution,par.1,par.2,true.score,n=1e6) {
  X <- RDF(distribution,n,par.1,par.2)
  X.prime <- RDF(distribution,n,par.1,par.2)
  mean(abs(X-true.score))-.5*mean(abs(X-X.prime))
}

out <- foreach(i=1:nrow(fcasts[!is.na(true.score)])) %dopar% {
  fcasts[i,GneitingCRPS(dist,par.1,par.2,true.score,n=1e6)]
}
fcasts[!is.na(true.score),S.R:=unlist(out)]
fcasts[!is.na(true.score), S.R.r := scaleUnit(rank(S.R)),by=ifp_id]

# save.image()

tmp <- fcasts[!is.na(true.score),S.R,by=c("screen_name","ifp_id","type","dist")]
tmp[,y:=scaleUnit(rank(S.R)),by=ifp_id]

library(lme4)
mod <- lmer(y~factor(type) + (1|ifp_id) + (1|dist), data=tmp)
summary(lm(y~type,tmp))
summary(mod)
tmp[,mean(y),by=c("type")]

unique(tmp$ifp_id)


tmp2 <- fcasts[!is.na(true.score),S.R,by=c("screen_name","ifp_id","type","dist","par.1","par.2")]
tmp2[,idx:=1:.N]
tmp2[,QDF(dist,.5,par.1,par.2),by=idx]
l

```

```{r, eval=FALSE}
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#### Consensus
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~

fcasts.closed <- fcasts[!is.na(Outcome)]

# First get 'Daily' forecasts
getDailySet <- function(fcasts, 
                        ifp,
                        decay.recent=.5, 
                        decay.min.days=3) {
  myifp <- fcasts[ifp_id==ifp,]
  bin.id <- paste0("bin_",1:13)
  ctpt.id <- paste0("ctpt_",1:12)

  min.date <- myifp[,min(as.Date(fcast_date))]
  max.date <- myifp[,as.Date(date_closed[1])]


  # Get distributions for every live day of the forecast
  roll <- foreach(d=seq.Date(min.date,max.date,"day")) %dopar% {
    # filter to forecasts made on or before d
    tmp <- myifp[as.Date(fcast_date)<=d,]

    # Keep only the most recent forecast by each user
    setkey(tmp, fcast_date)
    tmp <- tmp[idx %in% tmp[, list(last_fcast = tail(idx,n = 1)),
               by=user_id]$last_fcast]

    # get N by condition
    N <- tmp[,.N,by=type]
    # Keep only the newest forecasts
    # Either by using the decay.recent parameter and keeping the most recent X% of forecasts
    N[, n.keep.decay:=as.integer(N*decay.recent)]
    # or the number of forecasts made in the last N days as specificed by decay.min.days
    N[, n.keep.daymin:= tmp[,sum(as.Date(fcast_date)>(d-decay.min.days)),by=type]$V1]
    # whichever is larger
    N[, n.keep := max(n.keep.decay, n.keep.daymin),by=type]
    # unless N <= 5
    N[, n.keep:=ifelse(N<=5,N,n.keep)]
    N[, first:=(N-n.keep)+1]
    N[, last:=N]
    setkey(N,type)
    # print(N)
    tmp2 <- tmp[0,]
    for(condition in N$type) {
        tmp2 <- rbind(tmp2,tmp[type==condition,][N[condition,]$first:N[condition,]$last,])    
    }
    tmp2[,.N,by=type]
    tmp <- tmp2
    tmp[,roll.date:=d]
  }
  do.call(rbind,roll)
}

daily.set <- foreach(ifp=unique(fcasts.closed$ifp_id), .combine="rbind") %dopar% {
  getDailySet(fcasts, ifp)
}

daily.set[,fcast_date:=as.Date(fcast_date)]

updateGammas <- function(daily.set, n.bins=20) {
  # Subset to forecasts that need to be updated
  # forecasts made on the same day as the roll date are fine
  # and only gammas are updated
  updates <- daily.set[dist=="gamma" & (fcast_date!=roll.date),]

  # Define refitting cutpoints for each forecast
  ctpts <- data.table(matrix(NA_real_, nrow=nrow(updates), ncol=n.bins))
  bins <- copy(ctpts)
  bin.id <- paste0("bin_",1:20)
  ctpt.id <- paste0("ctpt_",1:20)
  setnames(ctpts, ctpt.id)
  setnames(bins, bin.id)
  updates <- cbind(updates[,list(idx,ifp_id,dist,par.1,par.2,fcast_date, roll.date, type)],bins,ctpts)  
  updates[, row.id:=1:.N]  

  # Obtain probabilities for each bin
  updates[,c(bin.id):=as.list((pgamma(seq(roll.date-fcast_date, 
                                       qgamma(.9999,par.1,par.2), 
                                       length=20),par.1,par.2) - 
                                pgamma(roll.date-fcast_date, par.1, par.2)) / 
                                as.numeric(1-pgamma(roll.date-fcast_date, par.1, par.2))),
       by=row.id]

  # Convert to interval probabilities     
  updates[,c(bin.id):=as.list(updates[,bin.id,with=FALSE] - 
                              cbind(0,updates[,bin.id[-length(bin.id)],with=FALSE]))]

  # Get cutpoints
  updates[,c(ctpt.id):=as.list(seq(as.numeric(roll.date-fcast_date), 
                                   qgamma(.9999,par.1,par.2), 
                                   length=20)-as.numeric(roll.date-fcast_date)),
           by=row.id]

  # Drop unnecessary 1st ctpt/bin
  updates[,bin_1:=NULL]
  updates[,ctpt_1:=NULL]

  # refit parameters to new, renormed probabilities
  new.fits <- foreach(i=1:nrow(updates)) %dopar% {
    bin.vals <- unlist(updates[i, .SD, .SDcols=bin.id[-1]])
    ctpt.vals <- unlist(updates[i, .SD, .SDcols=ctpt.id[-1]])
    dist.name <- updates[i,]$dist
    
    tryCatch({
      if(abs(round(sum(bin.vals),2)-1)<.01) {
        fit <- FitFnInterval(probs  = bin.vals,     
                             quants = ctpt.vals,
                             dist.name = dist.name)
        return(data.table(par.1 = fit[1],
                          par.2 = fit[2],
                          sse  = fit[3]))      
      } else {
        return(data.table(par.1 = NA_real_,
                          par.2 = NA_real_,
                          sse  = NA_real_))
      }
    },
    error=function(cond){
      return(data.table(par.1 = NA_real_,
                        par.2 = NA_real_,
                        sse  = NA_real_))
    })
  }
  new.fits <- do.call(rbind,new.fits)
  daily.set[dist=="gamma" & (fcast_date!=roll.date), 
            c("par.1","par.2","sse"):=new.fits]
  return(daily.set)
}

daily.set <- updateGammas(daily.set)


#### Get Rolling Consensus
# Theta-M


ThetaM <- daily.set[,list(par.1=median(par.1, na.rm=TRUE),
                          par.2=median(par.2, na.rm=TRUE),
                          true.score=Outcome[1],
                          dist=dist[1],
                          ctpts=ctpts[1],
                          N=.N),
                    by=c("roll.date","ifp_id","type")]
ThetaM[dist=="gamma", true.score:=true.score-as.numeric(roll.date)]

# Score ThetaM
ThetaM[dist=="beta", true.score:=true.score/100]
GneitingCRPS("beta",40,73,.447,n=1e6)

out <- foreach(i=1:nrow(ThetaM)) %dopar% {
  ThetaM[i,GneitingCRPS(dist,par.1,par.2,true.score,n=1e6)]
}

ThetaM[,S.R:=unlist(out)]
ThetaM[is.na(S.R),.N,]
ThetaM[, S.R.r := rank(S.R),by=c("ifp_id","roll.date")]

ThetaM[,sum(S.R.r==1)/(.N),by=c("type")]
ThetaM[,sum(S.R.r==2)/(.N),by=c("type")]
ThetaM[,sum(S.R.r==3)/(.N),by=c("type")]
ThetaM[,mean(S.R.r),by=c("type","ifp_id")]

fcasts[ifp_id=="1410-0",]
ThetaM[ifp_id=="1410-0",]

ThetaM.MD <- ThetaM[,list(S.R=mean(S.R)),by=c("ifp_id","type")]
ThetaM.MD[,S.R.r:=rank(S.R),by=c("ifp_id")]

library(ordinal)
fm1 <- clm(ordered(S.R.r)~factor(type, levels=c("fixed","random","user")), data=ThetaM.MD)
summary(fm1)

# fixed < user
# random ~< user

save.image(file="IARPA.Rdata")
```

```{r, results='asis', cache=FALSE}
load("../IARPA.Rdata")
```

## Forecaster Level

### Effect of conditions (None)

```{r, results='asis'}
library(stargazer)
library(lme4)
tmp$type <- factor(tmp$type, levels=c("random","user","fixed"))
mod1 <- lmer(y~factor(type) + (1|ifp_id) + (1|dist), data=tmp)
tmp$type <- factor(tmp$type, levels=c("user","fixed","random"))
mod2 <- lmer(y~factor(type) + (1|ifp_id) + (1|dist), data=tmp)
stargazer(mod1, mod2, type="html")
```

## Consensus Level

### Effect of conditions (Random < Fixed < User)


```{r}

ThetaM.MD <- ThetaM.MD[!(ifp_id %in% c("1530-6","1534-6","1536-6"))]


```

```{r, results='asis'}
library(ordinal)


xtabs(~ S.R.r+ type , data = ThetaM.MD[ifp_id%in%c(MDBS.ex[type=="random"]$ifp_id)][ifp_id!="1522-0"])



fm1 <- clm(ordered(S.R.r)~factor(type, levels=c("fixed","random","user")), data=ThetaM.MD)
fm2 <- clm(ordered(S.R.r)~factor(type, levels=c("random","user","fixed")), data=ThetaM.MD)
fm3 <- clm(ordered(S.R.r)~factor(type, levels=c("user","fixed","random")), data=ThetaM.MD)
stargazer(fm1, fm2, fm3, type="html")


```

```{r}
pdata.fm1 <- as.data.table(xtabs(~ S.R.r+ type , data = ThetaM.MD))
ggplot(data=pdata.fm1, aes(x=S.R.r, y=N, fill=type)) +
  geom_bar(stat="identity", position="dodge", color="black")

```


```{r, eval=FALSE}
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#### Brier Scores
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
extremize <- function(dist,par.1,par.2,k=1) {
  switch(dist,
         gamma = {
           mu <- par.1/par.2
           v <- k*par.1/par.2^2
           beta <- mu/v
           alpha <- v*beta^2
           list(alpha,beta)
         },
         normal = {
           alpha <- par.1
           beta <- par.2*k
           list(alpha,beta)
         },
         beta = {
           mu <- par.1/(par.1+par.2)
           v <- k*(par.1*par.2)/((par.1+par.2)^2*(par.1+par.2+1))
           alpha <- (((1-mu)/v)-(1/mu))*mu^2
           beta <- (((1-mu)/v)-(1/mu))*mu*(1-mu)
           list(alpha,beta)
         })
}

blah <- function(dist,par.1,par.2) {
  switch(dist,
         gamma = {
           mu <- par.1/par.2
           v <- par.1/par.2^2
           v
         },
         normal = {
          par.2
         },
         beta = {
           mu <- par.1/(par.1+par.2)
           v <- (par.1*par.2)/((par.1+par.2)^2*(par.1+par.2+1))
           v
         })
}


BS <- function(dist, par.1, par.2, ctpt, true.score) {
  round(2*(CDF(dist, ctpt, par.1, par.2)-(true.score<ctpt))^2,4)
}
vec.BS <- Vectorize(BS)

# Fix date formats
ThetaM[,ctpts:=gsub("/","-",ctpts)]
#
ThetaM[dist=="beta",true.score:=true.score/100]
setkey(ThetaM,ifp_id)

# get GJP cutpoints
id <- unique(ThetaM$ifp_id)[2]
id <- "1489-6"
ThetaM[ifp_id==id,ctpts:="2015-03-01|2015-05-31"]

id <- "1493-6"

ThetaM[,unique(ctpts),by=ifp_id]
id <- "1494-0"
ThetaM[ifp_id==id, ctpts:="03/31/15"]


MDBS <- foreach(id=unique(ThetaM$ifp_id)) %do% {
  tryCatch({
    score.cut <- unlist(ThetaM[id,][1,strsplit(ctpts,"|",fixed=TRUE)])
    if(ThetaM[id,]$dist[1]=="gamma") {
      if(grepl("^..-",score.cut[1])) {
        score.cut <- sapply(score.cut, function(s) {
          tmp <- unlist(strsplit(s,"-",fixed="TRUE"))
          paste(paste0("20",tmp[3]),
                ifelse(nchar(tmp[1])==1,paste0("0",tmp[1]),tmp[1]),
                ifelse(nchar(tmp[2])==1,paste0("0",tmp[2]),tmp[2]),
                sep="-")
        })
      }
      if(grepl("/",score.cut[1])) {
        score.cut <- sapply(score.cut, function(s) {
          tmp <- unlist(strsplit(s,"/",fixed="TRUE"))
          paste(paste0("20",tmp[3]),
                ifelse(nchar(tmp[1])==1,paste0("0",tmp[1]),tmp[1]),
                ifelse(nchar(tmp[2])==1,paste0("0",tmp[2]),tmp[2]),
                sep="-")
        })
      }

      score.cut <- unlist(sapply(score.cut, as.Date))
      score.cut <- foreach(sc=score.cut, .combine="cbind") %do% {
        matrix(sc-as.numeric(ThetaM[id,]$roll.date), ncol=1)
      }
    } else {
      score.cut <- matrix(as.numeric(rep(score.cut, times=nrow(ThetaM[id,])), ncol=1))
    }

    out <- apply(score.cut,2, function(ct) {
      ThetaM[id, list(dist=dist, 
                      type=type,
                      BS=vec.BS(dist, par.1, par.2, ct, true.score),
                      N=N)]
    })
    out <- out[[1]]
    out[,list(BS=round(mean(BS, na.rm=TRUE),4),
              N=mean(N)),by=c("type","ifp_id","dist")] 
  }, error = function(cond) {
    data.table(type=NA,ifp_id=id,dist=ThetaM[id,]$dist[1],BS=NA,N=NA)
  })
}
MDBS <- do.call(rbind,MDBS)

MDBS[ifp_id=="1494-0"]

ThetaM[,row.id:=1:nrow(ThetaM)]
ThetaM[,v:=blah(dist,par.1,par.2),by=row.id]
ThetaM[,sd(v),by=ifp_id]
ThetaM[,c("alpha","beta"):=extremize(dist,par.1,par.2,1),by=row.id]
MDBS.ex <- foreach(id=unique(ThetaM$ifp_id)) %dopar% {
  tryCatch({
    score.cut <- unlist(ThetaM[id,][1,strsplit(ctpts,"|",fixed=TRUE)])
    if(ThetaM[id,]$dist[1]=="gamma") {
      if(grepl("^..-",score.cut[1])) {
        score.cut <- sapply(score.cut, function(s) {
          tmp <- unlist(strsplit(s,"-",fixed="TRUE"))
          paste(paste0("20",tmp[3]),
                ifelse(nchar(tmp[1])==1,paste0("0",tmp[1]),tmp[1]),
                ifelse(nchar(tmp[2])==1,paste0("0",tmp[2]),tmp[2]),
                sep="-")
        })
      }
      if(grepl("/",score.cut[1])) {
        score.cut <- sapply(score.cut, function(s) {
          tmp <- unlist(strsplit(s,"/",fixed="TRUE"))
          paste(paste0("20",tmp[3]),
                ifelse(nchar(tmp[1])==1,paste0("0",tmp[1]),tmp[1]),
                ifelse(nchar(tmp[2])==1,paste0("0",tmp[2]),tmp[2]),
                sep="-")
        })
      }

      score.cut <- unlist(sapply(score.cut, as.Date))
      score.cut <- foreach(sc=score.cut, .combine="cbind") %do% {
        matrix(sc-as.numeric(ThetaM[id,]$roll.date), ncol=1)
      }
    } else {
      score.cut <- matrix(as.numeric(rep(score.cut, times=nrow(ThetaM[id,])), ncol=1))
    }

    out <- apply(score.cut,2, function(ct) {
      ThetaM[id, list(dist=dist, 
                      type=type,
                      BS=vec.BS(dist, alpha, beta, ct, true.score),
                      N=N)]
    })
    out <- out[[1]]
    out[,list(BS=round(mean(BS),4),
              N=mean(N)),by=c("type","ifp_id","dist")] 
  }, error = function(cond) {
    data.table(type=NA,ifp_id=id,dist=ThetaM[id,]$dist[1],BS=NA,N=NA)
  })
}
MDBS.ex <- do.call(rbind,MDBS.ex)

tmp1 <- copy(MDBS.ex)
tmp2 <- copy(MDBS.ex)
tmp1[,inf:=1]
tmp2[,inf:=3]
MDBS.ex <- rbind(tmp1,tmp2)
MDBS.ex[ifp_id=="1415-0"]
ThetaM[ifp_id=="1415-0"]

MDBS.ex[type=="random",]

MDBS.ex[ifp_id=="1494-0"]
ThetaM[ifp_id=="1494-0"]

save.image("IARPA.Rdata")

MDBS.ex[BS==0,]
MDBS.ex[ifp_id=="1451-6",]
ThetaM[ifp_id=="1451-6"]

```

```{r, eval=FALSE}
rollers <- copy(all.fits)
rollers <- rollers[type %in% c("rolling","rollingCtl")]

# merge with ifp.data
# ifp.data <- ifp.data[IFPID!="1419"]
setkey(rollers, ifp_idx)
setkey(ifp.data, IFPID)
rollers <- ifp.data[rollers]

names.bins <- grep("bin_", names(rollers), fixed=TRUE, value=TRUE)
names.ctpts <- grep("ctpt_", names(rollers), fixed=TRUE, value=TRUE)

# Convert date outcomes to numeric
rollers[dist=="gamma" & Outcome!="",Outcome:=as.numeric(as.Date(Outcome))]
rollers[, Outcome:=as.numeric(Outcome)]

# Remove any foracsts without specified outcomes
# fcasts <- fcasts[!is.na(Outcome),]
# fcasts[,Outcome:=as.numeric(Outcome)]


# Error
rollers[,SS.tot:=2*apply(rollers[,.SD,.SDcols=names.ctpts],1,var,na.rm=TRUE)]
rollers[, SS.fit := SS.tot - sse]
rollers[, R.sq := 1-(sse/SS.tot)]

# Convert date outcomes to numeric
rollers[dist=="gamma",Outcome:=as.numeric(as.Date(Outcome))]
rollers[,unique(Outcome),by=c("ifp_id")]

# Remove any foracsts without specified outcomes
rollers <- rollers[!is.na(Outcome),]
rollers[,Outcome:=as.numeric(Outcome)]

# Check outcome verses medians as sanity check
rollers[,est.median:=QDF(dist,.5,par.1,par.2),by=1:nrow(rollers)]
rollers[,list(median(est.median),Outcome[1]),by=ifp_id][4:36,round(.SD,3),.SDcols=c("V1","V2")]

rollers[,list(est=round(median(est.median),digits=10),
             out=round(median(Outcome), digits=2)),by=ifp_id]


# Error
rollers[,SS.tot:=2*apply(rollers[,.SD,.SDcols=names.ctpts],1,var,na.rm=TRUE)]
rollers[, SS.fit := SS.tot - sse]
rollers[, R.sq := 1-(sse/SS.tot)]

# Drop 'unfittable'
rollers <- rollers[sse!=42,]
# Drop neg Rsq
rollers <- rollers[R.sq>0,]

# Adjust outcome (true.score) for date IFPs by date forecast made, and betas
rollers[value_type=="date",true.score:=Outcome-as.numeric(as.Date(fcast_date))]
rollers[value_type!="date",true.score:=Outcome]
rollers[dist=="beta",true.score:=Outcome/100]

# Drop forecasts made after close
rollers <- rollers[as.Date(date_closed)>=as.Date(fcast_date)]

# FOR SOME REASON MANY DATE FORECASTS HAVE NEGATIVE CUTPOINTS... WTF? FIND OUT WHY
rollers <- rollers[!(dist=="gamma" & ctpt_0<0)]

rollers <- rollers[!is.na(true.score)]
rollers[,unique(ifp_id)]

out <- foreach(i=1:nrow(rollers)) %dopar% {
  rollers[i,GneitingCRPS(dist,par.1,par.2,true.score,n=1e6)]
}
rollers[,S.R:=unlist(out)]
rollers[is.na(S.R),.N,by=c("type")]
rollers[, S.R.r := scaleUnit(rank(S.R)),by=ifp_id]

tmp.roll <- rollers[,mean(S.R),by=c("screen_name","ifp_id","type","dist")]
tmp.roll[,y:=scaleUnit(rank(V1)),by=ifp_id]

library(lme4)
mod.roll <- lmer(y~factor(type) + (1|ifp_id), data=tmp.roll)
summary(mod.roll)
summary(lm(y~type,tmp.roll))

tmp[,mean(y),by=c("type","ifp_id")]


tmp[,median(y),by=c("type","ifp_id")]
tmp[,median(y),by=c("type")]

####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#### Consensus
####~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~


# First get 'Daily' forecasts
getDailySet <- function(fcasts, 
                        ifp,
                        decay.recent=.5, 
                        decay.min.days=3) {
  myifp <- fcasts[ifp_id==ifp,]
  bin.id <- paste0("bin_",1:13)
  ctpt.id <- paste0("ctpt_",1:12)

  min.date <- myifp[,min(as.Date(fcast_date))]
  max.date <- myifp[,as.Date(date_closed[1])]


  # Get distributions for every live day of the forecast
  roll <- foreach(d=seq.Date(min.date,max.date,"day")) %dopar% {
    # filter to forecasts made on or before d
    tmp <- myifp[as.Date(fcast_date)<=d,]

    # Keep only the most recent forecast by each user
    setkey(tmp, fcast_date)
    tmp <- tmp[idx %in% tmp[, list(last_fcast = tail(idx,n = 1)),
               by=user_id]$last_fcast]

    # get N by condition
    N <- tmp[,.N,by=type]
    # Keep only the newest forecasts
    # Either by using the decay.recent parameter and keeping the most recent X% of forecasts
    N[, n.keep.decay:=as.integer(N*decay.recent)]
    # or the number of forecasts made in the last N days as specificed by decay.min.days
    N[, n.keep.daymin:= tmp[,sum(as.Date(fcast_date)>(d-decay.min.days)),by=type]$V1]
    # whichever is larger
    N[, n.keep := max(n.keep.decay, n.keep.daymin),by=type]
    # unless N <= 5
    N[, n.keep:=ifelse(N<=5,N,n.keep)]
    N[, first:=(N-n.keep)+1]
    N[, last:=N]
    setkey(N,type)
    # print(N)
    tmp2 <- tmp[0,]
    for(condition in N$type) {
        tmp2 <- rbind(tmp2,tmp[type==condition,][N[condition,]$first:N[condition,]$last,])    
    }
    tmp2[,.N,by=type]
    tmp <- tmp2
    tmp[,roll.date:=d]
  }
  do.call(rbind,roll)
}

daily.set <- foreach(ifp=unique(rollers$ifp_id), .combine="rbind") %do% {
  getDailySet(rollers, ifp)
}

daily.set[,fcast_date:=as.Date(fcast_date)]

updateGammas <- function(daily.set, n.bins=20) {
  # Subset to forecasts that need to be updated
  # forecasts made on the same day as the roll date are fine
  # and only gammas are updated
  updates <- daily.set[dist=="gamma" & (fcast_date!=roll.date),]

  # Define refitting cutpoints for each forecast
  ctpts <- data.table(matrix(NA_real_, nrow=nrow(updates), ncol=n.bins))
  bins <- copy(ctpts)
  bin.id <- paste0("bin_",1:20)
  ctpt.id <- paste0("ctpt_",1:20)
  setnames(ctpts, ctpt.id)
  setnames(bins, bin.id)
  updates <- cbind(updates[,list(idx,ifp_id,dist,par.1,par.2,fcast_date, roll.date, type)],bins,ctpts)  
  updates[, row.id:=1:.N]  

  # Obtain probabilities for each bin
  updates[,c(bin.id):=as.list((pgamma(seq(roll.date-fcast_date, 
                                       qgamma(.9999,par.1,par.2), 
                                       length=20),par.1,par.2) - 
                                pgamma(roll.date-fcast_date, par.1, par.2)) / 
                                as.numeric(1-pgamma(roll.date-fcast_date, par.1, par.2))),
       by=row.id]

  # Convert to interval probabilities     
  updates[,c(bin.id):=as.list(updates[,bin.id,with=FALSE] - 
                              cbind(0,updates[,bin.id[-length(bin.id)],with=FALSE]))]

  # Get cutpoints
  updates[,c(ctpt.id):=as.list(seq(as.numeric(roll.date-fcast_date), 
                                   qgamma(.9999,par.1,par.2), 
                                   length=20)-as.numeric(roll.date-fcast_date)),
           by=row.id]

  # Drop unnecessary 1st ctpt/bin
  updates[,bin_1:=NULL]
  updates[,ctpt_1:=NULL]

  # refit parameters to new, renormed probabilities
  new.fits <- foreach(i=1:nrow(updates)) %dopar% {
    bin.vals <- unlist(updates[i, .SD, .SDcols=bin.id[-1]])
    ctpt.vals <- unlist(updates[i, .SD, .SDcols=ctpt.id[-1]])
    dist.name <- updates[i,]$dist
    
    tryCatch({
      if(abs(round(sum(bin.vals),2)-1)<.01) {
        fit <- FitFnInterval(probs  = bin.vals,     
                             quants = ctpt.vals,
                             dist.name = dist.name)
        return(data.table(par.1 = fit[1],
                          par.2 = fit[2],
                          sse  = fit[3]))      
      } else {
        return(data.table(par.1 = NA_real_,
                          par.2 = NA_real_,
                          sse  = NA_real_))
      }
    },
    error=function(cond){
      return(data.table(par.1 = NA_real_,
                        par.2 = NA_real_,
                        sse  = NA_real_))
    })
  }
  new.fits <- do.call(rbind,new.fits)
  daily.set[dist=="gamma" & (fcast_date!=roll.date), 
            c("par.1","par.2","sse"):=new.fits]
  return(daily.set)
}

daily.set <- updateGammas(daily.set)


ThetaM.roll <- daily.set[,list(par.1=median(par.1, na.rm=TRUE),
                          par.2=median(par.2, na.rm=TRUE),
                          true.score=Outcome[1],
                          dist=dist[1],
                          ctpts=ctpts[1],
                          N=.N),
                    by=c("roll.date","ifp_id","type")]
ThetaM.roll[dist=="gamma", true.score:=true.score-as.numeric(roll.date)]

# Score ThetaM
out.roll <- foreach(i=1:nrow(ThetaM.roll)) %dopar% {
  ThetaM.roll[i,GneitingCRPS(dist,par.1,par.2,true.score,n=1e6)]
}

ThetaM.roll[,S.R:=unlist(out)]
ThetaM.roll[is.na(S.R),.N,]
ThetaM.roll[, S.R.r := rank(S.R),by=c("ifp_id","roll.date")]

ThetaM.roll[,sum(S.R.r==1)/(.N),by=c("type")]
ThetaM.roll[,sum(S.R.r==2)/(.N),by=c("type")]
ThetaM.roll[,sum(S.R.r==3)/(.N),by=c("type")]
ThetaM.roll[,mean(S.R.r),by=c("type","ifp_id")]

ThetaM.MD.roll <- ThetaM.roll[,list(S.R=mean(S.R)),by=c("ifp_id","type")]
ThetaM.MD.roll[,S.R.r:=rank(S.R),by=c("ifp_id")]

fm1.roll <- clm(ordered(S.R.r)~factor(type), data=ThetaM.MD.roll)
summary(fm1.roll)

xtabs(~S.R.r+type, data=ThetaM.MD.roll)
save.image(file="IARPA.Rdata")


ThetaM.roll[,row.id:=1:nrow(ThetaM.roll)]
ThetaM.roll[,v:=blah(dist,par.1,par.2),by=row.id]
ThetaM.roll[,sd(v),by=ifp_id]
ThetaM.roll[,c("alpha","beta"):=extremize(dist,par.1,par.2,1),by=row.id]

ThetaM.roll[ifp_id=="1489-6",ctpts:="2015-03-01|2015-04-30"]

id <- "1489-6"

MDBS.roll.ex <- foreach(id=unique(ThetaM.roll$ifp_id)) %dopar% {
  tryCatch({
    score.cut <- unlist(ThetaM.roll[id,][1,strsplit(ctpts,"|",fixed=TRUE)])
    if(ThetaM.roll[id,]$dist[1]=="gamma") {
      if(grepl("^..-",score.cut[1])) {
        score.cut <- sapply(score.cut, function(s) {
          tmp <- unlist(strsplit(s,"-",fixed="TRUE"))
          paste(paste0("20",tmp[3]),
                ifelse(nchar(tmp[1])==1,paste0("0",tmp[1]),tmp[1]),
                ifelse(nchar(tmp[2])==1,paste0("0",tmp[2]),tmp[2]),
                sep="-")
        })
      }
      if(grepl("/",score.cut[1])) {
        score.cut <- sapply(score.cut, function(s) {
          tmp <- unlist(strsplit(s,"/",fixed="TRUE"))
          paste(paste0("20",tmp[3]),
                ifelse(nchar(tmp[1])==1,paste0("0",tmp[1]),tmp[1]),
                ifelse(nchar(tmp[2])==1,paste0("0",tmp[2]),tmp[2]),
                sep="-")
        })
      }

      score.cut <- unlist(sapply(score.cut, as.Date))
      score.cut <- foreach(sc=score.cut, .combine="cbind") %do% {
        matrix(sc-as.numeric(ThetaM.roll[id,]$roll.date), ncol=1)
      }
    } else {
      score.cut <- matrix(as.numeric(rep(score.cut, times=nrow(ThetaM.roll[id,])), ncol=1))
    }

    out <- apply(score.cut,2, function(ct) {
      ThetaM.roll[id, list(dist=dist, 
                      type=type,
                      BS=vec.BS(dist, alpha, beta, ct, true.score),
                      N=N)]
    })
    out <- out[[1]]
    out[,list(BS=round(mean(BS),4),
              N=mean(N)),by=c("type","ifp_id","dist")] 
  }, error = function(cond) {
    data.table(type=NA,ifp_id=id,dist=ThetaM.roll[id,]$dist[1],BS=NA,N=NA)
  })
}
MDBS.roll.ex <- do.call(rbind,MDBS.roll.ex)

tmp1 <- copy(MDBS.roll.ex)
tmp2 <- copy(MDBS.roll.ex)
tmp1[,inf:=1]
tmp2[,inf:=3]
MDBS.roll.ex <- rbind(tmp1,tmp2)


save.image(file="IARPA.Rdata")


```



